---
title: "Data Visualizations"

---

## The first plot


## Plot of my country
Some time ago, I was interested in maps using R. I found some information with some libraries that can be used. The idea is to understand that we need to plot coordinates in a plot. In this small example I plot the map of Ecuador

```{r , message=FALSE}
library(maptools)
library(RColorBrewer)
my.palette1 <- brewer.pal(n = 12, name = "Set3")
crswgs84=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
provincias<-readShapePoly("C:/Users/lenovo/Desktop/Msc.Statistics/Blog/sanmath.github.io/SHP/nxprovincias.shp")
plot(provincias,col=my.palette1)
```
Is the summer in Switzerland, we can see the temperature in the most important cities here. Bern, Geneva and Zúrich. Finally , we can include the information and show in a map.

```{r , message=FALSE}
library(weatherData)
library(sp)
library(maptools)
library(RColorBrewer)

crswgs84=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
cantones<-readShapePoly("C:/Users/lenovo/Desktop/Msc.Statistics/Blog/sanmath.github.io/SHP/CHE_adm1.shp")

mycols <- colors()[round(runif(25,100,130))]
mycols<-heat.colors(25)
mycols[c(6,8,25)]<-"tomato4"

plot(cantones,col=mycols,main="Switzerland Temperature Summer")

zh<-getCurrentTemperature("LSZH")[,c(2)]
br<-getCurrentTemperature("LSZB")[,c(2)]
gnv<-getCurrentTemperature("LSGG")[,c(2)]


text(coordinates(cantones)[c(6,8,25),],
     labels = c(paste("Bern",br,"°"),
                paste("Geneva",gnv,"°"),
                paste("Zúrich",zh,"°")),cex = 0.8)

```

